What public transit API logs tell us about travel flows

### 2016-01-08 paper.tex
Title changed and subsections introduced in relwork
Chord diagram, added reference in section 4.2

\title{Studying public transit API query logs\\ to get an indication of travel flows}
\numberofauthors{6}
\author{
\alignauthor
Pieter Colpaert\\
\affaddr{\email{\texttt{pieter.colpaert@ugent.be}}}
\and
\alignauthor
Alvin Chua\\
\affaddr{\email{\texttt{alvin.chua@asro.kuleuven.be}}}
\and
\alignauthor
Ruben Verborgh\\
\affaddr{\email{\texttt{ruben.verborgh@ugent.be}}}
\and
\alignauthor
Erik Mannens\\
\affaddr{\email{\texttt{erik.mannens@ugent.be}}}
\and
\alignauthor
Rik Van de Walle\\
\affaddr{\email{\texttt{rik.vandewalle@ugent.be}}}
\and
\alignauthor
Andrew Vande Moere\\
\affaddr{\email{\texttt{andrew.vandemoere\\@asro.kuleuven.be}}}\\
}

@@

\section{Related work}
\label{sec:relwork}

@@

@@

@@

\subsection{Visualization}\label{sec:vis}
%Flow visualizations are commonly employed to facilitate the comparison of aggregated movement. 
The chord diagram is a visualization technique based on the node-link metaphor that arranges nodes along the circumference of a circle. 
Each node is represented by an arc where its length is proportional to the total volume of incoming and outgoing flows. 
Chords or curved line segments are drawn to connect nodes. 
The width at the head or tail of each chord indicates the amount of movement relative frequency of movement from a certain location to another.
In our implementation of the chord diagram, nodes are colour coded to indicate individual provinces and the major cities located within their administrative boundaries. 
Interactive filtering is introduced to simplify the visualization and details are provided in pop-up dialogue when upon mouse-over.

>>>>

\title{What public transit API logs tell us about travel flows}
\numberofauthors{6}
\author{
\alignauthor
Pieter Colpaert\\
\affaddr{\email{\texttt{pieter.colpaert@ugent.be}}}
\and
\alignauthor
Alvin Chua\\
\affaddr{\email{\texttt{alvin.chua@asro.kuleuven.be}}}
\and
\alignauthor
Ruben Verborgh\\
\affaddr{\email{\texttt{ruben.verborgh@ugent.be}}}
\and
\alignauthor
Erik Mannens\\
\affaddr{\email{\texttt{erik.mannens@ugent.be}}}
\and
\alignauthor
Rik Van de Walle\\
\affaddr{\email{\texttt{rik.vandewalle@ugent.be}}}
\and
\alignauthor
Andrew Vande Moere\\
\affaddr{\email{\texttt{andrew.vandemoere\\@asro.kuleuven.be}}}\\
}

@@

\section{Related work}
\label{sec:relwork}
%\subsection{Flow analysis}

@@

\subsection{Studying Query Logs}

@@

\subsection{Visualizing Travel Flows}

@@

\subsection{Visualization}\label{sec:vis}
%Flow visualizations are commonly employed to facilitate the comparison of aggregated movement. 
The chord diagram is a visualization technique based on the node-link metaphor that arranges nodes along the circumference of a circle \cite{krzywinski2009circos}. 
Each node is represented by an arc where its length is proportional to the total volume of incoming and outgoing flows. 
Chords or curved line segments are drawn to connect nodes. 
The width at the head or tail of each chord indicates the amount of movement relative frequency of movement from a certain location to another.
In our implementation of the chord diagram, nodes are colour coded to indicate individual provinces and the major cities located within their administrative boundaries. 
Interactive filtering is introduced to simplify the visualization and details are provided in pop-up dialogue when upon mouse-over.
